Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
add Dan Gunter's talk

\item \textbf{Dan Gunter, Sarah Poon and Lavanya Ramakrishnan: \textit{Bringing the
User into Building Sustainable Software for Science}}

>>>>

\item \textbf{Dan Gunter, Sarah Poon and Lavanya Ramakrishnan: \textit{Bringing the
User into Building Sustainable Software for Science}}
``What is needed to develop sustainable software'' is the main question in Dan
Gunter's talk. Above the usual suspects of funding, great developers, good
design, and software engineering practices, however, Dan Gunter places the
users. He explains this using a traditional software development model starting
from gathering requirements, and reaching release through a design and
development and testing phase. The main defficiency that with this approach is
pointed out to be the too-late interaction with users. Instead, an alternative
approach is proposed that, at first, skips the development phase and repeatedly
goes through requirement gatherning, design and user interaction/learning
phases, and only eventually starts development once an agreement is reached,
leading to an increased user satisfaction, higher adoption, and eventually to
systained software.
